{ \normalsize Master Thesis} \\ Bluetooth Low Energy Supported Indoor Location

### 2017-03-06 paper.tex
New section order . 6/3

%% ADD Generic Problems (i.e. using smartphone)
%  3 vectors: technology (beacons) , loc description , loc calculation

@@

% Describe generic solution
The Idealized generic architecture , which can be seen on figure \ref{fig:generic}, was created with the intention of providing a common ground for any systems which planned to have an indoor location based on a smartphone, which allows interoperability among those who make use of it, while presenting a way to structure the system so that the impact on the smartphone is reduced. If one analyses it according to the three points presented in figure \ref{fig:choices}, one can say that by having dedicated serves for the location computation and the location description instead of having it locally on the smartphone, interoperability is highly improved. This setup allows for systems to implement whichever algorithm they intent for as long as the server is capable of distinguishing which algorithm is to be used, responsability which is passed onto the smartphone. In scenarios of interoperability, the smartphone should be able to use any of its sensors to capture data, dealing with the technology component, and tag them before sending it for computation on the server. The location description is contained on the map server and it is up to the system to choose which one to utilise, be it self-created or owned by a third party such as google maps or openstreet maps. For as long as the smartphone is aware of the type of location that he is to receive, interoperability should be achieved.

@@

%into
In this chapter one will first analyse the systems that layed the foundations of indoor location systems in section \ref{subsec:dedicated}, in order to study systems that were fully dependant on having specific hardware for obtaining user location. Section \ref{subsec:gentech} will present the technlogies that are compatible with modern day smartphones, analyse its pros and cons and mention existant projects based on them. The following section, \ref{subsec:technique} will describe the existent ways of obtaining the data that is required for infering a user's location as well as the techniques that make use of them. To conclude, on section \ref{subsec:desciption}, one will present the existent ways of describing locations through system that make use of them.

@@

\section{Architecture}
\label{sec:architecture}

@@

\section{Implementation}
\label{sec:struture}

\subsection{Bluetooth Low energy}
\label{ble}

@@

\subsection{ BLE beacon}
\label{subsec:beacon}

@@

\subsection{ Server}
\label{subsec:server}

@@

\subsection{ Application}
\label{subsec:app}

@@

\section{Performance Analysis}
\label{sec:performance}

@@

>>>>

@@

The Idealized generic architecture , which can be seen on figure \ref{fig:generic}, was created with the intention of providing a common ground for any systems which planned to have an indoor location based on a smartphone, which allows interoperability among those who make use of it, while presenting a way to structure the system so that the impact on the smartphone is reduced. If one analyses it according to the three points presented in figure \ref{fig:choices}, one can say that by having dedicated serves for the location computation and the location description instead of having it locally on the smartphone, interoperability is highly improved. This setup allows for systems to implement whichever algorithm they intent for as long as the server is capable of distinguishing which algorithm is to be used, responsability which is passed onto the smartphone. In scenarios of interoperability, the smartphone should be able to use any of its sensors to capture data, dealing with the technology component, and tag them before sending it for computation on the server. The location description is contained on the map server and it is up to the system to choose which one to utilise, be it self-created or owned by a third party such as google maps or openstreet maps. For as long as the smartphone is aware of the type of location that he is to receive, interoperability should be achieved.

@@

In this chapter one will first analyse the systems that layed the foundations of indoor location systems in section \ref{subsec:dedicated}, in order to study systems that were fully dependant on having specific hardware for obtaining user location. Section \ref{subsec:gentech} will present the technlogies that are compatible with modern day smartphones, analyse its pros and cons and mention existant projects based on them. The following section, \ref{subsec:technique} will describe the existent ways of obtaining the data that is required for infering a user's location as well as the techniques that make use of them. To conclude, on section \ref{subsec:desciption}, one will present the existent ways of describing locations through system that make use of them.

@@

\section{GEFILOC}
\label{sec:system}

% Resume

\subsection{Deployment environment}
\label{subsec:deployment}

In order to understand how a system based on this generic architecture, figure \ref{fig:generic} has to be strutured, it is of relevance to analyse the system component's description and requirements that would allow it to be deployed. If one starts by analysing the beacons component, one can describe them as the reference points of the system which are in charge of providing nearby users with information relative to their surroundings. These beacons are always ready and available to the users and upon being contacted, they should inform the smartphone which has initiated the communication of the address of the beacon's associated location server. Since the beacon only communicates with the smartphone, it isn't required to have any other communication capacity other than that specific to its technology. The last requirement is that the beacon needs to be uniquely identified and have the address of its associated server, while being capable of transmitting that same information to the smartphone.

The smartphone service is the component that is in charge of communicating with both the beacons and the location server. This service is a software component of the smartphone application which is available to being called when a location is requested. Once a location is requested by the application, the service should communicate with nearby beacons through one of its sensors. A service is associated with one and only one technology, as such if the application is to support more than one technlogy, multiple services should be implemented. This condition is relevant since the required sensor depends on the chosen technology and because it allows the service to quickly associate the data that it is collecting with the technology, information which must be delivered to the location server. Once the beacon data has been collected, the same data is forwarded to the beacon's associated server, together with a tag representing the technology of the beacons. Upon obtaining a location, the service should forward the data to the application, which is responsible of later communicating with the map server. In terms of requirements, the service needs to have Wi-Fi or at least 3G available for communicating with both the location and maps server, and access to the sensor required to communicate with the nearby beacon, for BLE it would be the bluetooth antenna or for QR it would be the camera.

The Location server should have a database of all the devices associated to it, each with its exact location of the map. This location is dependent on the method for location description chosen, i.e. latitude/longitude or x/y. The server should also be able to take input from any of the supported technologies, depends on the beacons in the database, in order to output the user's location. From this description one can define the requirements of the location server as having in storage the beacons that are associated it as well as their location, being capable of communicating with the smartphone application and being in accordance with the map server, achieved through providing location description that is the same as that present in the maps server.

The Map server is responsible for providing the application with the maps that it has requested. The only decision concerning this server is the type of location description that is to be used and consequently the only requirement is that it has to be in accordance with the information on the location server.

\subsection{Architecture}
\label{subsec:architecture}

@@

\subsection{Implementation}
\label{sec:struture}

\subsubsection{Bluetooth Low energy}
\label{ble}

@@

\subsubsection{ BLE beacon}
\label{subsec:beacon}

@@

\subsubsection{ Smartphone service}
\label{subsec:service}

\subsubsection{ Server}
\label{subsec:server}

@@

\subsection{Evaluation}
\label{sec:eval}

@@

%% Qualitativamente 
%% graficos e tal

@@

%% Qualitativamente

Although a complete implementation of the proposed architecture was achieved for BLE, one must indicate the required changes that would be necessary to make when change one or several parts of the system. The parts that can be changed are the three possibilities previously studied from figure \ref{fig:choices}. In case the technlogy is to be change, we will use QR code as an example, the affected areas are the beacons, the smartphone service and the location server. By changing the to QR code, the technology changes instantly as there is no more requirement for BLE beacons but instead there will be QR codes placed in fixed places. Each QR code would be required contain information about its associated server. The service would change the mechanism utilised to collect data, instead of listening for BLE beacons through its bluetooth antenna, it will open up the camera, so that the user can capture the QR code which would then be forwarded to the location server. The location server would have to be prepared for receiving the QR data and obtaining the location relative to that QR code.

If the system were to be changed on the location algorithm component, this would only require changes on the location server. The algorithms connection has only two connections points with the system, the data that it receives and the location it outputs. As such, for as long as the new algorithm makes use of the same data and in the end, once it has concluded, it outputs one location of the same format, no other issue should surface.

A modification on the location description utilised would have an impact on both the location and map server. With such a request, the map server is required to change completely the stored maps in order to support the new description method, while the changes on the location server are on the database, since the location of the beacons should change, and on the way the location algorithm processes these same locations.
